---
title: "Impact of Google Translation Project on Telugu Wikipedia"
author: "Arjuna Rao C"
date: "June 22, 2015"
output: html_document
---
##Raw data and preprocessing
Raw data for this project comes from the following sources.

###Wikipedia Editing statistics
* https://stats.wikimedia.org/EN/TablesWikipediaTE.htm
From this, extract the table Monthly counts & Quarterly rankings: May 2015 into a spreadsheet. Delete the quarterly portion, update the column headings to incorporate the details from the heading rows

###Wikipedia page view information

### Page requests for specific pages
* http://stat.grok.se gives pageviews for a specifc month
* Make use of script updatepvdata.R to obtain pageviews for a set of articles in a month.
* Input file should have header page_title and then one page name without quotes and with spaces transformed to underscore per line.
* This gives the total page_requests and the month specification. for details see the script
* Usage: updatepvdata("te","<src file>","<yyyymm eg:201403>","<result file>")

### Identifying Google Translation Project pages
Google Translate updates are marked by a field like the follwing in the comment field. Sometimes the updates could be done anonymously and sometimes the % translation also could be missing. Some translations may have been done by volunteer wikimedians to experiment with Google Translate tool. Sometimes, Google contributors have overwritten pages already existing, without checking.

So to ascertain  the number of articles contributed by  GTP, the following procedure is used.

Obtain the list of articles with the revision comment containing 'toolkit': 1991 (as on 3 May 2015, Quarry link http://quarry.wmflabs.org/query/3579)

### Identifying Featured article pages
The talk pages of featured articles are gathered into a category called  "ఈ_వారం_వ్యాసాల_చర్చలు_-_%". Use this information to get the list of articles and their featured year, week information.
http://quarry.wmflabs.org/query/3556

### Page requests for the entire wiki
https://stats.wikimedia.org/EN_India/TablesPageViewsMonthlyMobile.htm
Specifically do the following for non mobile normalized views and mobile normalized views.
As the html page is populated by a script, the information is difficult to extract directly. Copy paste  page requests table to a spreadsheet and take out the column corresponding to Telugu language. Then extract the relevant number.

Then combine the page requests information into a common data frame. Alternately combined normalised page requests information can be  obtained similarly and used when analysing the total page views.


## Data processing
### code samples
### for gtp language wikipedia plots.
```{r, cache=TRUE}
library(ggplot2)
gtplang<-read.csv("data/gtplang.wsv",header=TRUE,sep="\t")
g<-ggplot(gtplang,aes(Wikipedia,GTP.articles,fill=Wikipedia))+geom_bar(stat="identity")+geom_text(label=paste(gtplang$Wikipedia,gtplang$GTP.articles,sep="\n"),vjust=c(rep(1.1,4),-0.5))+labs(x=" ",y="Number of articles",title="Google Translation Project in Indian language wikipedias")+  scale_colour_manual(values=cbPalette)+theme(legend.position="none",axis.text.x=element_blank())
g
```
###Key Editing statistics 
```{r, cache=TRUE}
library(ggplot2)
library(reshape2)
source("src/convert wiki stats to numbers.R")
ws<-prepwstats()
mindex<-c(as.Date("2007-06-15"),as.Date("2008-06-15"),as.Date("2009-06-15"),as.Date("2010-06-15"),as.Date("2011-06-15"),as.Date("2012-06-15"))
cindex<-c("month","wikipedians_tot","db_size_words_M")
wsgtp<-ws[ws$month %in% mindex,cindex]
print(wsgtp)
source("src/pctcompute.R")
wspct<-as.data.frame(pctcompute(wsgtp))
wspct$month<-wsgtp$month
wspct<-wspct[-dim(wsgtp)[1],]
wspctm<-melt(wspct,id.vars="month",measure.vars=c("wikipedians_tot","db_size_words_M"))
g<-ggplot(wspctm,aes(as.factor(strftime(month,"%Y/%m")),value,group=variable))+
  geom_line(aes(color=variable))+labs(x="Year/month",y="Pecentage yearly change",title="Telugu Wikipedia - Wikipedians and Project Size \n Impact of Google Translation Project")+
  geom_vline(xintercept=2,color="red",linetype=4)+geom_vline(xintercept=4,color="red",linetype=4)+
  scale_colour_manual(name="",values=c("blue","black"),
      breaks=c("wikipedians_tot", "db_size_words_M"),
      labels=c("Number of Wikipedians", "Project size(Mwords)"))+
  theme(legend.justification=c(0.0,0.0), legend.position=c(0.68,0.7))
g
```

###Page views 
```{r, cache=TRUE}
source("src/tepvplot.R")
g<-plot_gtp_pr()
g
```

###Popularity
```{r, cache=TRUE}
#GTP page requests total
gtppr201403<-read.csv("data/gtppr201403.wsv",header=TRUE,sep=" ")
sum(gtppr201403$page_requests)
#non GTP featured article page requests total
falpr201403<-read.csv("data/falpr201403.wsv",header=TRUE,sep=" ")
sum(falpr201403$page_requests)
```

###Popularity of bot created pages
```{r, cache=TRUE}
vilsamp1pr<-read.csv("data/vilsamp1pr.csv",header=TRUE,sep=" ")
hist(vilsamp1pr$page_requests,main="Bot created article page requests",ylab="Number of pages",xlab="page requests in March 2014")
# mean and sd of 1000 samples of bot created pages
mn<-mean(vilsamp1pr$page_requests)
sd<-sd(vilsamp1pr$page_requests)
cat("mean:",mn,"standard deviation:",sd,sep=" ")
#95% Confidence intervals for mean
cat("95% confidence interval for mean:")
mn+c(-1,1)*qt(0.975,999)*sd(vilsamp1pr$page_requests)/sqrt(1000)
```
##References
1) http://stat.grok.se for page requests in any given month for an article
2) http://quarry.wmflabs.org for an easy to use and share query interface for wikipedia
3) http://stats.wikimedia.org for wikipedia editing statistics